---
title: "Practicing with Survival Analysis"
author: "Lisa Oshita"
date: "July 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### importing/setting up data, creating survival object
```{r}
#import data
dir <- file.path(getwd(),"data")
out <- read.csv(file.path(dir, "answers_data.csv"))

#creating time to event variable
out$time_until_answer <- out$first_answer_date - out$post_date
#filling in the NAs
empty <- which(is.na(out$time_until_answer))
for (i in empty) {
  out$time_until_answer[i] <- out$download_date[i] - out$post_date[i]
}

#subsetting to include only observations in english with positive time to event values
library(dplyr)
out_english <- out %>% 
          tbl_df() %>% 
          filter(langid == "en") %>%
          filter(time_until_answer > 0)

library(survival)

#creating survival object
surv_object <- Surv(out_english$time_until_answer, out_english$answered, type = "right")
```

### km estimator
* to do KM estimate for different groups: survfit(surv_object ~ category_to_groupby)
* confidence intervals: CI for S(t) are pointwise intervals
* can use log-log approach (specify conf.type = "log-log") to prevent upper limits from exceeding 1
```{r}
#KM estimator based on log-log approach
KM.obj <- survfit(surv_object ~ 1, conf.type = "log-log")
str(KM.obj)
summary(KM.obj)

#defining tick marks for x-axis
min <- min(out_english$time_until_answer)
max <- max(out_english$time_until_answer)

#cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/15), tick = TRUE, las = 2) #adding more detailed x axis
#lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
#lines(cb$time, cb$upper, lty=3, type="s")

#zoomed in to see behavior 
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xlim = c(0, 100000), xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/1000), tick = TRUE, las = 2)

plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xlim = c(100000, 1000000), xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/100), tick = TRUE, las = 2)
```

### instantaneous hazard using epiR package
* epi.isthaz function computes instantenous hazard based off of KM survival function
```{r}
library(epiR)
h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
head(h.hat)
#hazard = 4.3e-6 at time = 30 seconds
#interpretation: Questions who have not been answered by 30 seconds, are expected to be answered 4.3e-6 times in the next 2 seconds 

#par(mfrow = c(1,3))
#h(t) plots
plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE, las = 2)

#zooming in to get a closer look
plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/60), tick = TRUE, las = 2)

#there is a spike in instantaneous hazard before 130,000 seconds

plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,130000), type = "s", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/200), tick = TRUE, las = 2)

```

### estimating the cumulative hazard function
* H(t) = −log S(t), or can use the Nelson-Aalen estimator
* no function in survival package to do this
* working with instructions from OpenIntro Survival analysis in r pdf 
```{r}
#Kaplan Meier estimator of cumulative hazard
fit <- summary(survfit(surv_object ~ 1))
H.hat <- -log(fit$surv)
H.hat <- c(H.hat, tail(H.hat, 1)) #all this did was repeat the last entry? 

#Nelson Aalen estimator
h <- fit$n.event / fit$n.risk
H.tilde <- cumsum(h)
H.tilde <- c(H.tilde, tail(H.tilde, 1))

#plotting both KM and Nelson Aalen on same graph
min <- min(out_english$time_until_answer)
max <- max(out_english$time_until_answer)

plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s", xaxt = "n")
points(c(fit$time, 6500000), H.tilde, lty=2, type="s", xaxt = "n")
legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
axis(side = 1, at = seq(from = min, to = max, by = (max-min)/20), tick = TRUE, las = 2)
#KM and Nelson Aalen estimators look the same- because large data set? 
#Rate of increase in cumulative hazard spikes up drastically (immediately after question is posted)- indicating that hazard is increasing on that interval. Rate of increase in cumulative hazard after a certain point, levels out pretty quickly- indicating that hazard is decreasing
```

### mean, medians, percentiles 
```{r}
#to get mean and median
print(KM.obj, print.rmean=TRUE)

#finding percentiles 
quantile(KM.obj, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.75))
#getting NA for 0.75 because our lowest S(t) = 0.3410254
```

### comparing survival experiences between groups
```{r}
library(stringr)
library(rebus)

#comparing survival experiences for questions with/without "?"
#variable indicating if title contains questionmark 
out_english$contain_questionmark <- str_detect(out_english$title, pattern = QUESTION)
options(scipen=5)
KM_obj_question <- survfit(surv_object~contain_questionmark, data = out_english)
plot(KM_obj_question, lty = 1:2, xlab = "Time", ylab = "Survival Probability", main = "KM Curves for questions with and without a question mark")
legend("topright", c("False", "True"), lty = 1:2)
#for the log-rank test 
survdiff(surv_object~contain_questionmark, data = out_english)


#comparing survival experiences across product categories
colors <- c("antiquewhite", "aquamarine", "azure4", "black", "blue", "blue4","burlywood4", "chartreuse", "coral", "cornflowerblue", "darkgoldenrod1", "darkgreen", "darkolivegreen1", "darkorchid", "deeppink")
KM_obj_category <- survfit(surv_object~category, data = out_english)
plot(KM_obj_category, col = colors, xlab = "Time", ylab = "Survival Prob", main = "KM Curves by product category")
legend("topright", levels(out_english$category), col = colors, pch = 21, cex = 0.60)
survdiff(surv_object~category, data = out_english)

#comparing survival experiences across devices that were categorized correctly and those that were not
out_english$categorized <- 0
out_english$categorized[!is.na(out_english$category)] <- 1
KM_obj_correct <- survfit(surv_object ~ as.factor(categorized), data = out_english)
plot(KM_obj_correct, lty = 1:2, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for categorized variable")
legend("topright", c("0", "1"), lty = 1:2)
survdiff(surv_object~categorized, data = out_english)

#comparing survival experiences for number of tags included
KM_obj_tags <- survfit(surv_object~as.factor(n_tags), data = out_english)
plot(KM_obj_tags, col = 1:5, xlab = "Time", ylab = "Survival Prob", main = "KM Curves by number of tags included")
legend("topright", c("0", "1", "2", "3", "4"), col = 1:5, pch = 21)
survdiff(surv_object~as.factor(n_tags), data = out_english)


#comparing by title length intervals (no significant difference here)
#creating title length intervals
# out_english$title_length_intervals <- cut(as.numeric(out_english$title_length), breaks = 5)
# KM_obj_title <- survfit(surv_object~as.factor(out_english$title_length_intervals), data = out_english)
# plot(KM_obj_title, col = 1:5, xlab = "Time", ylab = "Survival Prob", main = "KM Curves by intervals of title length")
# legend("topright", levels(out_english$title_length_intervals), col = 1:5, pch = 21)
# survdiff(surv_object~as.factor(title_length_intervals), data = out_english)

#comparing survival between new/continuing users
KM_obj_users <- survfit(surv_object ~ as.factor(new_user), data = out_english)
plot(KM_obj_users, lty = 1:2, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for new/continuing users")
legend("topright", c("Continuing User", "New User"), lty = 1:2)
survdiff(surv_object~as.factor(new_user), data = out_english)

#comparing survival between number of pictures included
KM_obj_pic <- survfit(surv_object ~ as.factor(n_images), data = out_english)
plot(KM_obj_pic, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for n_images", col = colors)
legend("topright", levels(as.factor(out_english$n_images)), col = colors, pch = 21)
survdiff(surv_object ~ as.factor(n_images), data = out_english)

#looking at whether or not including at least 1 picture makes a difference
#creating the variable
out_english$pic_included <- 0
out_english$pic_included[out_english$n_images != 0] <- 1

KM_obj_pic1 <- survfit(surv_object ~ as.factor(pic_included), data = out_english)
plot(KM_obj_pic1, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for n_images", lty = 1:2)
legend("topright", c("0", "1"), lty = 1:2)
survdiff(surv_object ~ as.factor(pic_included), data = out_english)

#looking survival experiences between questions with "tried" and without
out_english$tried <- str_detect(as.character(out_english$text), or("tried", "searched"))
KM_obj_tried <- survfit(surv_object ~ as.factor(tried), data = out_english)
plot(KM_obj_tried, xlab = "Time", ylab = "Survival Prob", main = "KM Curves for questions with/without 'tried'", lty = 1:2)
legend("topright", c("0", "1"), lty = 1:2)
survdiff(surv_object ~ as.factor(tried), data = out_english)
```

### practicing with cox regression 
```{r}
coxph(formula = surv_object ~ category + contain_questionmark + n_tags + as.factor(new_user) + as.factor(pic_included), data = out_english)
```












  

