---
title: "stringr cheatsheet"
author: "Lisa Oshita"
date: "June 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basics
* writeLines(): default separates strings with a new line, use sep argument to change
* \\ : escape sequence
```{r}
format(1000000000, big.mark = ",", big.interval = 3, scientific = FALSE)
```
* formatC(): f for fixed, e for scientific, g for fixed unless scientific saves space
```{r}
x1 <- c(0.0011, 0.011, 1)
formatC(x1, format = "f", digits = 1)
```
* paste(): to put together strings

## stringr 
### str_c
like paste, but default separator is an empty string not a space
```{r}
library(stringr)
str_c(c("a","b","c"), "hi")
paste(c("a","b","c"), "hi")
```
### str_length
(also works on factors)
```{r}
str_length(c("hello", "hey", "what's up"))
```
### str_sub
extracts part of strings based on their location 
```{r}
str_sub(c("Bruce", "Wayne"), 1, 4)
str_sub(c("Bruce", "Wayne"), -4, -1)
```
### str_detect
Does the string contain the pattern? 
```{r}
pizzas <- c("cheese", "pepperoni", "sausage and green peppers")
str_detect(pizzas, pattern = fixed("pepper"))
```
### str_subset
detects strings with a pattern and then subsets it
```{r}
str_subset(pizzas, pattern = fixed("pepper"))
```
### str_count
counts number of times pattern occurs in each string
```{r}
str_count(pizzas, pattern = fixed("e"))
```
### str_split
* pull apart strings into more useful variables
* use simplify = TRUE to get a matrix with n columns as output (and not a list)
```{r}
date_ranges <- c("23.01.2017 - 29.01.2017", "30.01.2017 - 06.02.2017")
#as a list
str_split(date_ranges, pattern = fixed(" - "))
#as a matrix
split_dates_n <- str_split(date_ranges, pattern = fixed(" - "), simplify = TRUE, n = 2)
split_dates_n
```
### str_replace/str_replace_all
```{r}
phone_numbers <- c("510-555-0123", "541-555-0167")
#replace - with space
str_replace(phone_numbers, "-", " ")
str_replace_all(phone_numbers, "-", " ")
```
## Regular Expressions
### str_view
* %R% in rebus package gives you a way to combine regular expressions
* str_view is good for testing patterns, opens up an html window
* str_view_all to see all matching patterns
```{r}
library(rebus)
x2 <- c("cat", "coat", "scotland", "tic toc")
str_view(x2, pattern = START %R% "c")
```
### ANY_CHAR
```{r}
str_view(x2, pattern = "c" %R% ANY_CHAR %R% "t")
#match string with exactly 3 characters
str_view(x2, pattern = START %R% ANY_CHAR %R% ANY_CHAR %R% ANY_CHAR %R% END)
```
### str_extract
returns just the part of the string that matched the pattern
```{r}
pattern <- "c" %R% ANY_CHAR %R% "t"
str_extract(x2, pattern)
```
### or function in rebus
allows us to specify a set of alternatives 
```{r}
x3 <- c("grey sky", "gray elephant", "white elephant")
str_view(x3, pattern = or("grey", "gray"), match = TRUE)
#match = TRUE will only display elements that had a match
str_view(x3, pattern = "gr" %R% or("e", "a") %R% "y", match = TRUE)
```
### char_class
* way of specifying "match one (and only one) of the following characters"
* negated_char_class: any single character that isn't one of the following
```{r}
vowels <- char_class("AaEeIiOoUu")
str_view(x3, pattern = vowels)
str_view_all(x3, pattern = vowels)
```
### repetition
* one_or_more
* zero_or_more
* optional
```{r}
#negated char class that matches anything but a vowel
not_vowels <- negated_char_class("aeiouAEIOU")
#see items with only vowels
str_view(c("aaa", "aba", "dada", "ccc"), pattern = exactly(one_or_more(vowels)), match = TRUE)
#see items with no vowels 
str_view(c("aaa", "aba", "dada", "ccc"), pattern = exactly(one_or_more(not_vowels)), match = TRUE)
```
### example
```{r}
#pattern that matches 3 digits
three_digits <- DGT %R% DGT %R% DGT
four_digits <- three_digits %R% DGT
#separator pattern (character class that contains - . ( ) " ")
separator <- char_class("-.() ")
# Create phone pattern
phone_pattern <- optional(OPEN_PAREN) %R% 
  three_digits %R% 
  zero_or_more(separator) %R% 
  three_digits %R% 
  zero_or_more(separator) %R%
  four_digits
contact <- c("Call me at 555-555-0191", "123 Main St", "Phone: 555.555.0191 Mobile: 555.555.0192")
#test the pattern
str_view(contact, pattern = phone_pattern)
#extract phone numbers
str_extract(contact, phone_pattern)
#extract ALL phone numbers
str_extract_all(contact, phone_pattern)
```
### example 2
```{r}
#pattern to match 1 or 2 digits
age <- DGT %R% optional(DGT)
#pattern to match units
unit <- optional(SPC) %R% or("YO", "YR", "MO")
#can combine patterns
pattern = age %R% unit
```
## Advanced matching
### capture
used to capture part of a regular expression 
```{r}
email <- capture(one_or_more(WRD)) %R% "@" %R% one_or_more(WRD) %R% DOT %R% one_or_more(WRD) 
str_view("(wolverine@xmen.com)", pattern = email)
#using str_match allows you to access the captured piece
str_match("(wolverine@xmen.com)", pattern =  email)
```
### backreferences
* allow you to find repeated patterns or words
* requires: capture() and reference to it (REF1)
```{r}
str_view(c("hello", "sweet", "kitten"), pattern = capture(LOWER) %R% REF1)
#pattern to see repeated letters (ex: abab)
pair_of_repeated <- capture(lower(2)) %R% REF1
```
### replacing with backreferences
capture happens in pattern argument, backreference used in replacement argument
```{r}
x <- c("hello", "sweet", "kitten")
str_replace(x, capture(ANY_CHAR), str_c(REF1, REF1))

#pattern to match words ending in "ING"
pattern <- one_or_more(WRD) %R% "ING"
narratives <- "31 YOF FELL FROM TOILET HITITNG HEAD SUSTAINING A CHI "
# Test replacement
str_replace(narratives, capture(pattern), str_c("CARELESSLY", REF1, sep = " "))
```
### Unicode and patterns
* if code has more than 4 digits, use uppercase U - "\U..."
* as.hexmode(utf8ToInt("a")) to hexidecimal code for "a"
* stri_trans_ncf: composes characters with combining accents into a single character
* stri_trans_nfd: decomposes character with accents into separate letter and accent characters 
* match accents using rebus value - UP_DIACRITIC
```{r}
library(stringi)
library(stringr)
as.hexmode(utf8ToInt(stri_trans_nfd("\u00e8")))
as.hexmode(utf8ToInt(stri_trans_nfc("\u0065\u0300")))
```
### matching a single grapheme
* ANY_CHAR will only match character represented by single code point
* grapheme - represents a display character, but may be composed of many code points 
* use GRAPHEME to matche any grapheme
```{r}
x <- c("Adele", "Ad\u00e8le", "Ad\u0065\u0300le")
writeLines(x)
str_view(x, "Ad" %R% ANY_CHAR %R% "le")
str_view(x, "Ad" %R% GRAPHEME %R% "le")
```
### stri_isempty
* stringi function
* finds empty strings, returns logical 

### or1()
* function in rebus package
* specifies alternatives, can pass in a vector of alternatives (rather than each alternative being an argument)

### changing case to ease matching
* whole_word will only match if pattern occurs as a word on it's own
* will match "The cat" but not "caterpillar"
* str_to_upper to change all to uppercase, str_to_lower to change all to lowercase 
```{r}
x <- c("Cat", "CAT", "cAt") 
str_view(x, "cat")
str_view(str_to_lower(x), "cat")
```
### ignoring case when matching
regex function in stringr allows you to specify that matching should be case insensitive
```{r}
library(stringr)
library(stringi)
x <- c("Cat", "CAT", "cAt") 
str_view(x, pattern = regex("cat", ignore_case = TRUE), match = TRUE)
```

```{r}
str_view(c("a", "A"), pattern = regex("a", ignore_case = TRUE), match = TRUE)
```

### fixing case problems
* str_to_title transforms to title case 
* stringi function stri_trans_totitle allows specification of type (default = "word"), can also change to "sentence" 

















