---
title: "Writing Functions in R"
author: "Lisa Oshita"
date: "June 30, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Basics
* typeof() is basically same as class()
* initializing output vector for for loops: output <- vector("double", length)
* must use output[[i]] in the body (use double brackets)
* use seq_along in the indexing statement, safer

## Functional programming
### purr package
* all map functions take a vector as the first argument, and return function applied to each element of vector
* type of object returned is determined by the function suffix
* map() returns a list or data frame
* map_lgl() returns a logical vector
* map_int() returns a integer vector
* map_dbl() returns a double vector
* map_chr() returns a character vector
```{r}
library(nycflights13)
library(purrr)
#finds mean of each column 
map_dbl(planes, mean, na.rm = TRUE)
#finds columns in planes that are numeric
map_lgl(planes, is.numeric)
#finds the type of each column
map_chr(planes, typeof)
```

### passing anonymous functions
```{r}
#regression for each value of cyl in the mtcars data set 
#splits data set according to cyl values
cyl <- split(mtcars, mtcars$cyl)
#applies regression to each group by using and anonymous function
map(cyl, function(df) lm(mpg ~ wt, data = df))

#using formulas and shortcuts
map_dbl(cyl, function(df) mean(df$disp))
#shortcut
map_dbl(cyl, ~ mean(.$disp))
```

### shortcuts for subsetting elements
strings as shortcuts
```{r}
#regression results from example above
models <- map(cyl, ~ lm(mpg ~ wt, data = .))
#get the coefficients for each model
coefs <- map(models, coef)
#Use string shortcut to extract the wt coefficient 
map(coefs, "wt")
```
numeric vectors as shortcuts
```{r}
#pull out second element in coefs
map_dbl(coefs, 2)
```

### pipes
* pipe operator: %>% included in purrr package
* simplifies code
* x %>% f(y) is another way of writing f(x, y)
* left-hand side of the piping becomes the first argument in the function
```{r}
#without piping
cyl <- split(mtcars, mtcars$cyl) 
map(cyl, ~ lm(mpg ~ wt, data = .))
#with piping, read as: split the data frame mtcars on cyl, then use map() on the result
split(mtcars, mtcars$cyl) %>% 
  map(~ lm(mpg ~ wt, data = .))
#with more piping
mtcars %>% 
  split(mtcars$cyl) %>%
  map(~ lm(mpg ~ wt, data = .)) %>%
  map(coef) %>% 
  map_dbl("wt")
```

## Advanced inputs and outputs
### safely, possibly, quietly
* safely takes a function as an argument and returns a function as its output
* function that is returned is modified so that it never throws an error, and never stops your computation 
*always returns a list with 2 elements: result and error
```{r}
safe_readLines <- safely(readLines)
safe_readLines("http://example.org")
```

### using map safely
```{r}
urls <- list( example = "http://example.org", rproj = "http://www.r-project.org", asdf = "http://asdfasdasdkfjlda")
safe_readLines <- safely(readLines)

# Use the safe_readLines with map()
html <- map(urls, safe_readLines)
str(html)

# Extract the result from one of the successful elements
html[["example"]][["result"]]

# Extract the error from the element that was unsuccessful
html[["asdf"]][["error"]]
```

### transpose
reshapes a list so the inner-most level becomes the outer-most level
```{r}
str(transpose(html))
#extracts results and errors
res <- transpose(html)[["result"]]
errs <- transpose(html)[["error"]]

#create a logical vector that is true when errs is null 
is_ok <- map_lgl(errs, is_null)
#use to extract successful results
res[is_ok]
#extract input from unsuccessful results
urls[!is_ok]
```

### mapping over 2 arguments
The first two arguments to map2() are the objects to iterate over and the third argument is the function to apply
```{r}
# want to vary sample size and mean for rnorm
# Initialize n
n <- list(5, 10, 20)
mu <- list(1, 5, 10)
map2(n, mu, rnorm)
```

### mapping over more than 2 arguments
* pmap() takes a list of arguments as its input
* default: matches the elements of the list to the arguments in the function by position
* provide names in list to avoid positional matching
```{r}
n <- list(5, 10, 20)
mu <- list(1, 5, 10)
sd <- list(0.1, 1, 0.1)
pmap(list(n, mu, sd), rnorm)
```

### mapping over functions and their arguments
* invoke_map: first argument is a list of functions, second argument specifies the arguments to the functions
* in simplest case, all functions take same argument and can use (...) to pass to each function
```{r}
f <- list("rnorm", "runif", "rexp")

rnorm_params <- list(mean = 10)
runif_params <- list(min = 0, max = 5)
rexp_params <- list(rate = 5)
params <- list(rnorm_params, runif_params, rexp_params)

invoke_map(f, params, n = 5)
```

### walk
* operates just like map but is designed for functions that don't return anything
* use for functions with side effects like printing, plotting, saving
```{r}
#list of functions
f <- list(Normal = "rnorm", Uniform = "runif", Exp = "rexp")
#Define params
params <- list(Normal = list(mean = 10), Uniform = list(min = 0, max = 5), Exp = list(rate = 5))

#simulated samples
sims <- invoke_map(f, params, n = 50)

# Use walk() to make a histogram of each element in sims
walk(sims, hist)
```

### walking over 2 or more arguments
```{r}
#varying 2 arguments in the histogram made above (vary x and breaks)
#change from default to reasonable breaks for each histogram
breaks_list <- list(
  Normal = seq(6, 16, 0.5),
  Uniform = seq(0, 5, 0.25),
  Exp = seq(0, 1.5, 0.1)
)

walk2(sims, breaks_list, hist)
```

### walking with many arguments
* pwalk, works just like pmap
* first argument should be a list that relies on matching arguments by name (not position) for the function to be iterated over
* this code varies sims, breaks, and titles for each histogram
```{r}
#finds the breaks for any user specifed arg
find_breaks <- function(x) {
  rng <- range(x, na.rm = TRUE)
  seq(rng[1], rng[2], length.out = 30)
}
#uses map to iterate find_breaks over sims
nice_breaks <- map(sims, find_breaks)
nice_titles <- c("Normal(10, 1)", "Uniform(0, 5)", "Exp(5)")
#pwalk iterates over multiple arguments 
pwalk(list(x = sims, breaks = nice_breaks, main = nice_titles), hist, xlab = "")
```

### walking with pipes
```{r}
#summary uses as .f argument in map
sims %>%
  walk(hist) %>%
    map(summary)
```

## Robust functions
### stopifnot
* quick way to have your function stop if a condition is not met 
* takes logical expressions as arguments, if any are false an error will occur
```{r}
x <- c(NA, NA, NA)
y <- c( 1, NA, NA, NA)
#function counts how many shared NAs
# both_na <- function(x, y) {
#  stopifnot(length(x) == length(y))
#  sum(is.na(x) & is.na(y))
#}
#both_na(x, y)
```

### stop
allows you to specify a more informative error message
```{r}
#both_na <- function(x, y) {
#  if (length(x) != length(y)) {
#    stop("x and y must have the same length", call. = FALSE)
#  }  
#  sum(is.na(x) & is.na(y))
#}
```

### side effects
* Side effects describe the things that happen when you run a function that alters the state of your R session
* If foo() is a function with no side effects (a.k.a. pure), then when we run x <- foo(), the only change we expect is that the variable x now has a new value. No other changes to anything else... know exactly the changes to the state of the session just by reading the call to the function

## Different classes of functions
### unstable types
* type of return object depends on input (type inconsistent)
* sapply is an example of inconsistent type
* use purrr package and map functions instead of sapply
* or fail early if something goes wrong
* note: any() is useful in conditional statements
* flatten_chr takes a list, removes heirarchy and will return either a character string or error message (indicated by chr)

### nonstandard evaluation
* functions that reference variables in a non-standard wway
* if you do need to use non-standard evaluation functions, make sure you include checks
```{r}
#this function uses filter function in dplyr (which is NSE function) to subset data based off of a threshold value in the variable x
#code includes checks to make sure that x is in the dataframe, and that there is no variable called threshold in the df 

library(dplyr)
big_x <- function(df, threshold) {
  # Write a check for x not being in df
  if (!"x" %in% names(df)) { 
    stop("df must contain variable called x", call. = FALSE)
  }

  # Write a check for threshold being in df
  if ("threshold" %in% names(df)) {
    stop("df must not contain variable called threshold", call. = FALSE)
  }
  
  dplyr::filter(df, x > threshold)
}
```

### Hidden arguments
* hidden arguments are function inputs that may be different for different users or r sessions
* ex: argument defaults that depend on global options
* in general you want to avoid having the return value of your function depend on any global options
* it's okay to have side effects depend on global options (like printing output, calling the summary function on something...)


