---
title: "Data Visualization with ggplot2"
author: "Lisa Oshita"
date: "July 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Basics of ggplot2
```{r}
library(ggplot2)
#must tell ggplot that cyl is a categorical variable by wrapping it in factor, otherwise will treat it as numeric
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) + geom_point()
```

### Grammar of graphics
* data: the data to be plotted
* aesthetics: the scales onto which we map our data
* geometries: visual elements used for our data
* facets, statistics...
```{r}
#adding geom_smooth() would place a smoothed line over the points
ggplot(mtcars, aes(x = wt, y = mpg, color = disp, size = disp)) +
  geom_point() 
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point(alpha = 0.4)
```
* alpha controls transparency of points/lines...
* setting se = FALSE in geom_smooth layer will remove any error shading

```{r}
#DOESN'T OUTPUT THE SAME!!!!
ggplot(mtcars, aes(x = wt, y = mpg, col = cyl)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  geom_smooth(aes(group = 1), method = "lm", se = FALSE, linetype = 2)
```

### tidyr package
* a dataset is called tidy when every row is an observation and every column is a variable
* gather() function takes multiple columns and gathers them into a single column by adding rows
* separate() function splits one column into two or more columns according to a pattern you define
```{r}
library(tidyr)
#created a key column with gather, this column contains values like sepal.width..., want to separate this into part and measure
iris.tidy <- iris %>%
  gather(key, Value, -Species) %>%
  separate(key, c("Part", "Measure"), "\\.")
```

### aesthetics
* ONLY APPLICABLE TO CATEGORICAL VARIABLES
* color changes outline of points
* fill changes inside shading
* shape (default = 19) (shapes 1-20 can only accept a color aesthetic, shapes 21-25 can accept both color and fill aesthetics )
```{r}
#mapping a categorical variable to fill doesn't change the colors (legend is generated)
#use fill when you have another shape, or with shape = 21 (which has fill and color attribute)
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl, col = am)) +
  geom_point(shape = 21, size = 4, alpha = 0.6)

ggplot(mtcars, aes(x = wt, y = mpg, label = cyl)) +
  geom_text()
```

### attributes
* variables in a dataframe are mapped to aesthetics in ggplot statement, visual elements are set by attributes in geom layers
* if aesthetic and attribute are set with the same argument, attribute takes precedence
```{r}
#attributes in geom_point overwrite whats in aesthetics 
my_color <- "#4ABEFF"
ggplot(mtcars, aes(x = wt, y = mpg, color = cyl)) +
  geom_point(color = my_color)
#choosing different shape
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) +
  geom_point(size = 10, shape = 23, color = my_color)
```

### position
```{r}
cyl.am <- ggplot(mtcars, aes(x = factor(cyl), fill = factor(am)))
cyl.am +
  geom_bar(position = "dodge") 

#cleaning up axes with scale_ functions
val = c("#E41A1C", "#377EB8")
lab = c("Manual", "Automatic")
cyl.am +
  geom_bar(position = "dodge") +
  scale_x_discrete("Cylinders") + 
  scale_y_continuous("Number") +
  scale_fill_manual("Transmission", 
                    values = val,
                    labels = lab) 
```

### dummy aesthetic
```{r}
ggplot(mtcars, aes(x = mpg, y = 0)) +
  geom_jitter()

#add the function to change the y axis limits
ggplot(mtcars, aes(x = mpg, y = 0)) +
  geom_jitter() +
  scale_y_continuous(limits = c(-2,2))
```

### overplotting 
* can also use geom_jitter instead of geom_point
```{r}
ggplot(diamonds, aes(x = clarity, y = carat, color = price)) + 
  geom_point(alpha= 0.5)
#with jittering
ggplot(diamonds, aes(x = clarity, y = carat, color = price)) + 
  geom_point(alpha= 0.5, position = "jitter")
```

### histograms
* default bindwidth = range/30
* ..count.. is mapped to the y axis (stored in the internal dataframe)
* ..density.. is the proportional frequency of a bin in relation to the whole data set
```{r}
#fill argument stayes outside aes since it's an attribute and not an aesthetic mapping
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 1, aes(y = ..density..), fill = "#377EB8")
```

### position arguments (geom_hist/geom_bar)
* stack: place the bars on top of each other. Counts are used. This is the default position.
* fill: place the bars on top of each other, but this time use proportions.
* dodge: place the bars next to each other. Counts are used.
```{r}
#default
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) +
  geom_bar(position = "stack")
#fill
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) +
  geom_bar(position = "fill")
#dodge
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) +
  geom_bar(position = "dodge")

#position_dodge to be used when you want to specify how much dodging (same goes for position_jitter)
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) + 
  geom_bar(position = "dodge")
posn_d <- position_dodge(width = 0.2)
ggplot(mtcars, aes(x = as.factor(cyl), fill = as.factor(am))) + 
  geom_bar(position = posn_d, alpha = 0.6)
```

### overlapping histograms
```{r}
#default position is "stack"
ggplot(mtcars, aes(mpg, fill = as.factor(cyl))) +
  geom_histogram(binwidth = 1, position = "identity", alpha = 0.4)
#geom_freqpoly allows for overlapping (identity is the default)
ggplot(mtcars, aes(mpg, col = as.factor(cyl))) +
  geom_freqpoly(binwidth = 1)
```

### color ramps
* use scale_fill_brewer to set color palette (?brewer.pal for full list)
* use function colorRampPalette to generate all colors need 
* input is character vector of 2 or more color values (ex: #FFFFFF" (white) and "#0000FF" (pure blue))
* output is a function that takes one argument- the number of colors you want to extrapolate
```{r}
#working with Vocab dataframe from car package
library(car)

#this outputs an incomplete plot, since default gave has 9 colors, but variable has 11 categories
ggplot(Vocab, aes(x = education, fill = vocabulary)) +
  geom_bar(position = "fill") +
  scale_fill_brewer()

#Definition of a set of blue colors (from RColorBrewer package)
library(RColorBrewer)
blues <- brewer.pal(9, "Blues")
#makes a color range
blue_range <- colorRampPalette(blues)
#uses blue_range and scale_fill_manual to set color of bars
ggplot(Vocab, aes(x = as.factor(education), fill = as.factor(vocabulary))) +
  geom_bar(position = "fill") +
  scale_fill_manual(values = blue_range(11))

```

### line plots
* use geom_line()
* can use geom_rect to draw rectangles to highlight certain portions of a time-series line plot

### qplot
* good for simple plots
```{r}
qplot(wt, mpg, data = mtcars)

#categorical
qplot(wt, mpg, data = mtcars, size = factor(gear))
#continuous
qplot(wt, mpg, data = mtcars, color = hp)
#overplotting
qplot(x = factor(cyl), y = factor(vs), data = mtcars)
#using jitter to fix overplotting
qplot(x = factor(cyl), y = factor(vs), data = mtcars, geom = "jitter")

#dotplots (geom_dotplot uses a binning statistic)
ggplot(mtcars, aes(factor(cyl), wt, fill = factor(am))) +
  geom_dotplot(binaxis = "y", stackdir = "center")
#same plot with qplot()
qplot(
  factor(cyl), wt, 
  data = mtcars, 
  fill = factor(am), 
  geom = "dotplot", 
  binaxis = "y", 
  stackdir = "center"
)
```

### examples
```{r}
#ChickWeight dataset
ggplot(ChickWeight, aes(x = Time, y = weight, color = Diet)) + 
  geom_line(aes(group = Chick), alpha = 0.3) + 
  geom_smooth(lwd = 2, se = FALSE)
#titanic dataset 
library(titanic)
ggplot(titanic_train, aes(x = Pclass, fill = Sex)) + 
  geom_bar(position = "dodge") + 
  facet_grid(.~Survived)

posn.jd <- position_jitterdodge(0.5, 0, 0.6)
ggplot(titanic_train, aes(x = Pclass, y = Age, color = Sex)) + 
  geom_point(size = 3, alpha = 0.5, position = posn.jd) + 
  facet_grid(.~Survived)
```







